Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-02-27 paper/main.tex
adding some experiment writeups

The first experiment is designed to compare the two implementations of PALM
that solve a single large instance of the $\ell_1$-minimization problem (Algorithm \ref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ is known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.   
We also varied the different inner and tolerance levels from 1e-3 to 1e-6.
We averaged the the time taken for the ALM algorithm to solve 10 instances of a problem.

@@

The second experiment is to compare the amount of time to solve the face alignment
stage for each implementation.  Because the alignment stage is not affected by the resolution of the image,
we fix the resolution at 60x80.
{\bf VS:  this accuracy number depends on the number of subjects in the A matrix right?  So we either 
need to fix the number of subjects to compare against or vary it...}

The third experiment is to compare accuracy rate of the face recognition algorithm at different
image resolutions.

The fourth experiment is to compare the speed of the recognition stage w.r.t the number of 
subjects in the matrix $A$.

@@

We plot the resulted of the simulation benchmark below.  The x-axis represents the size of the 
$A$ and $A^TA$ matrix and the y-axis represents the average amount of time it to complete
a single problem instance.

The observations of this experiment are summarized below:
1.  With similar accuracy rates, the GPU implementation runs faster than the CPU when

>>>>

The first experiment is designed to compare the two implementations of PALM
that solve a single large instance of the $\ell_1$-minimization problem (Algorithm \ref{alg:alm}) by
comparing the amount of time to solve a problem given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit norm.  The ratio of $d:n$ varied from
$10:1$ to $10:5$ with the dimension of $d$ of matrix $A$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and normalized with unit norm.
Because the ground truth signal $\xx_0$ is known, the algorithm terminates
when $norm(\bx-\bx_0) < tolerance$.
The measurement vector was generated with the equation $\y_0 = A \x_0$.   
We also varied the different inner and outer tolerance levels from 1e-2 to 1e-5.
We averaged the the time taken for the ALM algorithm to solve 10 instances of a problem.

@@

The second experiment is to compare the amount of time to solve the face alignment
stage for each implementation.  Because the alignment stage is not affected by the resolution of the image,
we fix the resolution at 60x80.

Since we use a reduced training set for the recognition stage, our third experiment was to 
find the relationship between the probability that the true subject is in the training set vs the
 number of users in the reduced training set and the speed of the recognition stage w.r.t.
 the number of subjects in the training set.

The fourth experiment is to compare accuracy rate of the face recognition algorithm at different
image resolutions.  We fixed the number of users to be $enter here$ which was shown in figure  $enter here$  have 95\% probability
to have the true user in the training set, inner loop tolerance to 1e-2 and outer loop tolerance to 1e-3.

@@

We plot the most significant results of the simulation benchmark below.  The x-axis represents the size of the 
$A$ matrix and the y-axis represents the average amount of time it to complete a single problem instance.

The observations of this experiment are summarized below:
1.  With similar accuracy rates, the GPU implementation runs faster than the CPU at the crossover points 
noted on the plots.
2.  From the results, it was seen that tolerances...

\subsection{Face Alignment Benchmark}

\subsection{Face Recognition Benchmarks}
